---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# euissR

<!-- badges: start -->
<!-- badges: end -->

The goal of euissR is to make plotting coherent with the EUISS's visual identity
in ggplot2 less verbose. It provides functions for various pre-styled ggplot2 
geoms and color palettes for more streamlined plotting with ggplot2 in R.

euissR also comes with a custom ggplot2 theme that is set as default when
loading the package.

## Installation

You can install the development version of euissR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cdtrich/euissR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dplyr)
library(ggplot2)
library(euissR)

mtcars %>% 
  ggplot2::ggplot() +
  ggplot2::aes(wt, mpg) +
  geom_point_euiss() +
  geom_text_euiss(ggplot2::aes(label = wt))
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

If you include plots, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

## Fonts

euissR declares PT Sans Narrow as the default font as part of its custom
ggplot2 theme. It can be downloaded from [google fonts](https://fonts.google.com/specimen/PT+Sans+Narrow). If you don't want to 
use this font, set the `txt_family` value in `fonts.R` to another font name 
(one installed on your system), or delete the file and load the package
locally. 